Spikes demo

### 2018-11-06 analysis/spikesdemo.Rmd
Working on improvements to the Spikes demo; mainly in the setup instructions.

This small demonstration illustrates key features of the SMASH method
on a small, simulated data set with heteroskedastic variances. This
code implements the example given in Sec. 4.1 of the paper.

@@

Set up environment
------------------

@@

```{r load-pkgs, warning=FALSE}
library(ashr)
library(smashr)
library(scales)
library(ggplot2)
suppressMessages(library(cowplot))
source("../code/misc.R")
```

@@

>>>>

This small demonstration illustrates key features of the SMASH method
on a small, simulated data set with spatially structured variances. This
code implements the example presented in Sec. 4.1 of the paper.

@@

Initial setup instructions
--------------------------

To run this example on your own computer, please follow these setup
instructions. These instructions assume you already have R and/or
RStudio installed on your computer.

Download or clone the [git repository][smash-github] on your computer.

Launch R, and change the working directory to be the `analysis` folder
inside your local copy of the `smash-paper` git repository.

Install some of the packages used here, and in the code below:

```{r install-pkgs-1, eval=FALSE}
install.packages(c("devtools","ggplot2","cowplot"))
```

Finally, install the ashr and smashr packages from GitHub:

```{r install-pkgs-2, eval=FALSE}
library(devtools)
install_github("stephens999/ashr",upgrade_dependencies = FALSE,
               build_vignettes = TRUE)
install_github("stephenslab/smashr",upgrade_dependencies = FALSE,
               build_vignettes = TRUE)
```

Set up R environment
--------------------

@@

```{r load-pkgs, warning=FALSE, message=FALSE}
library(ashr)
library(smashr)
library(scales)
library(ggplot2)
library(cowplot)
source("../code/misc.R")
```

@@

[smash-github]: https://github.com/stephenslab/smash-paper
